Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-22 writing/DraftExposurePaper/DraftExposurePaper.Rmd
event count plots
fix typo

```{r}
#Top 2000 storm-county pairs for flooding events during tropical cyclones (since 1996)
flood_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "flood")
flood_2000 <- flood_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
flood_2000$value <- cut(flood_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_flood_2000 <- CountyChoropleth$new(flood_2000)
map_flood_2000$set_zoom(eastern_states)
map_flood_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_tornado_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Flood Events"
c <- map_flood_2000$render()
```

@@

>>>>

```{r}
#Top 2000 storm-county pairs for flooding events during tropical cyclones (since 1996)
flood_exposure <- county_events(counties = my_fips,
                              start_year = 1996, end_year = 2011,
                              event_type = "flood")
flood_2000 <- flood_exposure %>%
        slice(1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
flood_2000$value <- cut(flood_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_flood_2000 <- CountyChoropleth$new(flood_2000)
map_flood_2000$set_zoom(eastern_states)
map_flood_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_flood_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Flood Events"
c <- map_flood_2000$render()
```

@@

```{r}
#Event counts
grid.arrange(d, e, f, ncol = 1)
```
